Simple models of deliberated preference

### 2017-11-08 article.tex
Removed old incorrect basic encoding

\subsection{Encoding (non-intuitive)}
TODO…

To encode this data efficiently, we can define two binary relations $\prop^+$ and $\prop^−$: $(\ar, \ar') \in \prop^+$ ⇔ $(\ar, \ar')$ always supports $\prop$ sure or always supports both ⇔ $(\ar, \ar') \ileadsto \prop ∨ (\ar, \ar') \ileadsto b$; and $(\ar, \ar') \in \prop^− ⇔ (\ar, \ar') \ileadsto ¬\prop ∨ (\ar, \ar') \ileadsto b$.

This is indeed equivalent:
\begin{itemize}
	\item $(\ar, \ar') \ileadsto \prop ⇔ (\ar, \ar') \in \prop^+ ∧ (\ar, \ar') \notin \prop^−$
	\item $(\ar, \ar') \ileadsto ¬\prop ⇔ (\ar, \ar') \notin \prop^+ ∧ (\ar, \ar') \in \prop^−$
	\item $(\ar, \ar') \ileadsto b ⇔ (\ar, \ar') \in \prop^+ ∧ (\ar, \ar') \in \prop^−$
	\item $(\ar, \ar') \ileadsto \emptyset ⇔ (\ar, \ar') \notin \prop^+ ∧ (\ar, \ar') \notin \prop^−$
\end{itemize}

Here is a case where $\prop$ is possible but not strongly possible: $\exists (\ar_1, \ar) \ileadsto \prop$, $\exists (\ar_2, \ar) \ileadsto b$, $\nexists (\ar', \ar) \ileadsto ¬\prop$, $\nexists (\ar', \ar) \ileadsto \emptyset$. However this case is odd as just after showing $\ar_2$ to $i$ we could ask again about $\ar_1$ … (TODO)

Now do we have $\prop \in \isure ⇔ \exists \ar \suchthat \forall \ar': (\ar, \ar') \ileadsto \prop$?
\section{Todo}
\begin{itemize}
	\item If $i$ does not consider $\ar$ as supporting $\prop$, it also works: if $\prop$ is not weakly acceptable by default, then any $\ar'$ is considered by $i$ as a better argument than $\ar$ in favor of certain $¬\prop$, and so on. In fact, whether $\emptyset \ibeatse[\prop] \emptyset$ determines whether $\prop$ is weakly supported by default.
	\item I should define $\ar' (□\ibeatse[\prop]) \ar$ as an observable: “Assuming $\ar'$ would survive, do you consider $\ar'$ as leading to certainty of $¬\prop$, even when considering $\ar$?”. It distinguishes our knowledge and the truth: $\ar' (□\ibeatse[\prop]) \ar ⇒ \ar' \ibeatse[\prop] \ar$, thus, implies $¬ (\ar' \nibeatsst[\prop] \ar)$. But out of $¬ (\ar' (□\ibeatse[\prop]) \ar)$, nothing.
	\item Partition (objectively) $\allargs$ (or $\allargs × \alltopic$) into arguments in favor of $\prop, \text{sure}$, $¬\prop, \text{sure}$, and similarly for possible. Use only one rel $\ibeatse$, defined on contradictory arguments only, instead of $\ibeatse[\prop, \text{sure}]$ and others. Define $\ar' \ibeatse[\prop] \ar$ equals no when $¬(\ar' \ileadsto ¬\prop, \text{sure})$, equals $\ibeatse$ for adequate arguments, and equals yes when $¬(\ar \ileadsto \prop, \text{possible})$ and $\ar' \ileadsto ¬\prop, \text{sure}$, with probably some complications needed for the argument $\emptyset$ (and related default attitude towards $\prop$).
\end{itemize}

>>>>

\section{Todo}
\begin{itemize}
	\item If $i$ does not consider $\ar$ as supporting $\prop$, it also works: if $\prop$ is not weakly acceptable by default, then any $\ar'$ is considered by $i$ as a better argument than $\ar$ in favor of certain $¬\prop$, and so on. In fact, whether $\emptyset \ibeatse[\prop] \emptyset$ determines whether $\prop$ is weakly supported by default.
	\item I should define $\ar' (□\ibeatse[\prop]) \ar$ as an observable: “Assuming $\ar'$ would survive, do you consider $\ar'$ as leading to certainty of $¬\prop$, even when considering $\ar$?”. It distinguishes our knowledge and the truth: $\ar' (□\ibeatse[\prop]) \ar ⇒ \ar' \ibeatse[\prop] \ar$, thus, implies $¬ (\ar' \nibeatsst[\prop] \ar)$. But out of $¬ (\ar' (□\ibeatse[\prop]) \ar)$, nothing.
	\item Partition (objectively) $\allargs$ (or $\allargs × \alltopic$) into arguments in favor of $\prop, \text{sure}$, $¬\prop, \text{sure}$, and similarly for possible. Use only one rel $\ibeatse$, defined on contradictory arguments only, instead of $\ibeatse[\prop, \text{sure}]$ and others. Define $\ar' \ibeatse[\prop] \ar$ equals no when $¬(\ar' \ileadsto ¬\prop, \text{sure})$, equals $\ibeatse$ for adequate arguments, and equals yes when $¬(\ar \ileadsto \prop, \text{possible})$ and $\ar' \ileadsto ¬\prop, \text{sure}$, with probably some complications needed for the argument $\emptyset$ (and related default attitude towards $\prop$).
\end{itemize}
